Identification of high-yielding soybean lines with exceptional seed composition qualities

### 2022-05-10 doc/manuscript/manuscript.tex
Added to the step that makes heatmaps for phenotype average values across environments

Genotype & Value \textbackslash{}textsuperscript\{*\} & Rank\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}dag\} & Test Average\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}ddag\} & Check Average\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}S\} & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\

>>>>

Genotype & Value\textbackslash{}textsuperscript\{*\} & Rank\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}dag\} & Test Average\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}ddag\} & Check Average\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}S\} & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
